$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-01-27 paper/e6ssm-tuning-paper.tex
E6SSM --> E.

In this paper we investigate how big this tuning is if we bring this
scale all the way down to 20 TeV, effectively minimising contribution
from the stops. We find that the $Z^\prime$ limit is enough to already
require moderate fine tuning in the E6SSM.  We also show this is
comparable to the situation in the MSSM defined at the same scale if
chargino's could be ruled out below $700$ GeV.  We then show how this
tuning from the $Z^\prime$ mass looks for different $U(1)$ extensions,
finding that the current severity depends upon the charges but that
$Z^\prime$ limits are important in constraining the most natural
scenarios in all of these models.  Therefore the $Z^\prime$ constraint
is amongst the most important in terms of tuning and attacking natural
supersymmetry experimentally and the next run of the LHC will be
crucial in this respect.

@@

\begin{figure}
\begin{center}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_mssm_cutoff_scan_all_benchmark_points_tuning_vs_cutoff.png}} 
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
\\
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM1_all_tuning_data.png}}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM2_all_tuning_data.png}}%%
\caption{{\it Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in Table \ref{tab:benchmarks}.  {\it Top right panel:}  Individual sensitivities of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.  {\it Bottom left panel:} Individual sensitivities of E6SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.  {\it Bottom right panel:} Individual sensitivities of E6SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.    }
\label{Fig:BMs-varyMX}
\end{center}
\end{figure}

>>>>

In this paper we investigate how big this tuning is if we bring this
scale all the way down to 20 TeV, effectively minimising contribution
from the stops. We find that the $Z^\prime$ limit is enough to already
require moderate fine tuning in the E$_6$SSM.  We also show this is
comparable to the situation in the MSSM defined at the same scale if
chargino's could be ruled out below $700$ GeV.  We then show how this
tuning from the $Z^\prime$ mass looks for different $U(1)$ extensions,
finding that the current severity depends upon the charges but that
$Z^\prime$ limits are important in constraining the most natural
scenarios in all of these models.  Therefore the $Z^\prime$ constraint
is amongst the most important in terms of tuning and attacking natural
supersymmetry experimentally and the next run of the LHC will be
crucial in this respect.

@@

\begin{figure}
\begin{center}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_mssm_cutoff_scan_all_benchmark_points_tuning_vs_cutoff.png}} 
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
\\
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM1_all_tuning_data.png}}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM2_all_tuning_data.png}}%%
\caption{{\it Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in Table \ref{tab:benchmarks}.  {\it Top right panel:}  Individual sensitivities of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.  {\it Bottom left panel:} Individual sensitivities of E$_6$SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.  {\it Bottom right panel:} Individual sensitivities of E$_6$SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.    }
\label{Fig:BMs-varyMX}
\end{center}
\end{figure}
